---
title: "ShanklinHW3"
author: "Oliver Shanklin"
date: "February 26, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 1)

```{r}

vec_01 <- rnorm(10, mean = 0, sd = 1)
vec_1001 <- rnorm(10, mean = 100, sd = 1)
vec_10010 <- rnorm(10, mean = 100, sd = 10)
mean(c(vec_01, vec_1001, vec_10010))
sd(c(vec_01, vec_1001, vec_10010))


```

The mean and sd are not the exact same because we are sampling from those disatributions, but we are close since we are taking a sample.


## 2) 

```{r}

sample(c("heads", "tails"), 20, p = c(.5,.5), replace =T)


```

## 3) 

```{r}

set.seed(158)
sample(c("heads", "tails"), 20, p = c(.5,.5), replace =T)


```

set.seed(158) allows us to repeat the random sample with the exact same output.

## 4)


```{r}

x <- runif(20,-10,10)

y <- 75 + 2*x + 0.5*x^2 + 0.1*x^3

plot(x,y)

noise <- rnorm(20,0,5)

y_noise <- y + noise

plot(x,y_noise)

```

#### d) The plot is slightly different, where the scatter plot is not a perfect cubic funtion. There is a slight "noise" in the graph.

```{r}

noise_2 <- rnorm(20, 0, 50)

y_noise_2 <- y + noise_2

plot(x,y_noise_2)


```


#### e) There is a larger change in the graph because we are sampling from a normal with a larger sd, which means more variation in our noise plot.

```{r}
cbind(y, y_noise, y_noise_2)
```

#### f) There seems to be a much larger change in numbers because of the larger variation in the noise. So with more variation, there is a chance to have the noise farther away from "true"" y values.


