---
title: "STAT158HW5"
author: "Oliver Shanklin"
date: "April 12, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1)
#### a)

```{r}

jantemp <- read.csv("january_temp.csv", header = TRUE)
attach(jantemp)

plot(jantemp$Lat, jantemp$Long)

```



I was not sure what I was expecting for the plot.

### b)

```{r}

jantempLat <- lm(jantemp$JanTemp~jantemp$Lat)

plot(jantemp$JanTemp~jantemp$Lat)
abline(jantempLat$coefficients)

anova(jantempLat)
summary(jantempLat)

```

JanTemp = 108.73 - 2.11(Latitude)

$R^2$ is 0.7192


#### c)
```{r}


jantempLong <- lm(jantemp$JanTemp~jantemp$Long)

plot(jantemp$JanTemp~jantemp$Long)
abline(jantempLong$coefficients)

anova(jantempLong)
summary(jantempLong)



```

JanTemp = 24.571 + 0.0214(Longitude)

$R^2$ is 0.0005732

#### d)

It seems that the Latitude does a better job at predicting the tempurature since the $R^2$ value is closer to 1.

#### e)

```{r}

jantempLatLong <- lm(jantemp$JanTemp~jantemp$Lat+jantemp$Long)

anova(jantempLatLong)
summary(jantempLatLong)

```

$JanTemp = 98.64 - 2.16355(Lat) + 0.13396(Long)$

$R^2 = 0.7411$

The coefficient that changed the most was the Longitude. Up from 0.02.


#### f)

```{r}

jantempLatLongInt <- lm(jantemp$JanTemp~jantemp$Lat+jantemp$Long + jantemp$Lat*jantemp$Long)

anova(jantempLatLongInt)
summary(jantempLatLongInt)

```


$JanTemp = 259.48952 - 6.07(Lat) - 1.61(Long) + .042(Lat)(Long)$

$R^2 = 0.7939$

The $R^2$ Value did not change by much.

#### g)

Since I ran the anova command in each part here is the list of MSE.

51.2 for b), 182.228 for c), 48.1 for e), and 39.0 for f)

The closer to 0 that the r-squared is, the higher MSE is produced, and the farther away from 0, the MSE is lower.

## 2)


```{r}

t_stat <- numeric()

for(i in 1:10000){

  sample1 <- rnorm(10000,0,1)
  sample2 <- rnorm(10000,0,1)

  t_stat[i] <- t.test(sample1, sample2, var.equal = F)$statistic
}
#t_stat


hist(t_stat, freq = F)


```

## 3)

#### a)

```{r Problem3a}

t_stat2 <- numeric()

for(i in 1:10000){

  sample1 <- rnorm(100,0,1)
  sample2 <- rnorm(10,0,5)

  t_stat2[i] <- t.test(sample1, sample2, var.equal = F)$statistic
}
#t_stat


hist(t_stat2, freq = F)


```

This simulation produces a histogram very tall area around the mean, unlike 2) where it looked normal.


#### b)

```{r Problem3b}

t_stat3 <- numeric()

for(i in 1:10000){

  sample1 <- rnorm(100,0,1)
  sample2 <- rnorm(10,0,5)

  t_stat3[i] <- t.test(sample1, sample2, var.equal = TRUE)$statistic
}
#t_stat


hist(t_stat3, freq = F)


```

This histogram seems to be much wider with heavier tails.

